IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-04-11 codes/R/cohorts_nc.Rnw
add quantile differences decomposition

<<READ, cache=FALSE >>=
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/1_load.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/2_efa.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_main.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_fit.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/5_graphs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/6_ineq.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_graphs.R")

@@

>>>>

<<READ, cache=FALSE >>=
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/1_load.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/2_efa.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_main.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_fit.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/5_graphs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/6_ineq.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_graphs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_tabs.R")

@@

<<COUNTERF_PREP_TAB, dependson='COUNTERF'>>=
# prepare counterfactual tables
@

<<COUNTERF_INEQ, dependson='COUNTERF_PREP_TABS', results='markup'>>=
cat("Males EXT")
print(iqdecomp(logitcf.ext.m))

cat("Males INT")
print(iqdecomp(logitcf.int.m))

cat("Females EXT")
print(iqdecomp(logitcf.ext.f))

cat("Females INT")
print(iqdecomp(logitcf.int.f))
@
